Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2019-03-11 tex/main.tex
Reordered figures

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/air-exchange-rate/},
  {./../figures/kde-iacc-pressure/},
  {./../figures/simulation_predictions/},
  {./../figures/pair_grids/},
  {./../figures/multivariate_analysis/}
}
\usepackage{lineno}
\linenumbers
% macros

@@

\begin{figure}[!h]
		\centering
    \caption{Distributions of indoor/outdoor pressure differences (top row), and its correlation with indoor air contaminant concentrations (middle rows), and air exchange rate (bottom row), at three different VI sites - ASU house, Indianapolis site, and North Island NAS.}
    \label{fig:pair_grid}
    \includegraphics[width=\textwidth]{simple_grid.pdf}
\end{figure}

@@

@@

\begin{figure}[!h] % TODO: Adjust aspect ratio
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios_constant_ae}
  \includegraphics[width=0.5\textwidth]{land_drain_scenarios_constant_ae.pdf}
\end{figure}

@@

\begin{figure}[!h] % TODO: Adjust aspect ratio
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios_fluctuating_ae}
  \includegraphics[width=0.5\textwidth]{land_drain_scenarios_fluctuating_ae.pdf}
\end{figure}

@@

% New PP simulations with extreme Ae values for each pressure considered
% Now we capture most of the variability for open and closed
% Strong indicator that fluctating Ae is responsible for a significant portion of the variability
% Needs to be controlled better (hard)
% Or the span of values considered to give upper and lower limits on variability
% Use EPA handbook to estimate variability (pretty much can always be one OOM)

\begin{figure}[htb!] % TODO: Adjust aspect ratio
  \centering
  \caption{ (1D is 1 day, 2W is 2 weeks, and 3M is 3 months).}
  \label{fig:resampling}
  \includegraphics[width=0.5\textwidth]{temporal_variability/resampling.pdf}
\end{figure}

>>>>

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/2d_kde/},
  {./../figures/simulation_predictions/},
  {./../figures/pair_grids/},
  {./../figures/temporal_variability/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

\begin{figure}[!h]
		\centering
    \caption{Distributions of indoor/outdoor pressure differences (top row), and its correlation with indoor air contaminant concentrations (middle rows), and air exchange rate (bottom row), at three different VI sites - ASU house, Indianapolis site, and North Island NAS.}
    \label{fig:kde}
    \includegraphics[width=\textwidth]{nas_asu_pp.pdf}
\end{figure}

@@

\begin{figure}[htb!] % TODO: Adjust aspect ratio
  \centering
  \caption{ (1D is 1 day, 2W is 2 weeks, and 3M is 3 months).}
  \label{fig:resampling}
  \includegraphics[width=\textwidth]{temporal_variability/resampling.pdf}
\end{figure}

@@

\begin{figure}[!h] % TODO: Adjust aspect ratio
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios_fluctuating_ae}
  \includegraphics[width=\textwidth]{land_drain_scenarios_fluctuating_ae.pdf}
\end{figure}

\begin{comment}
\begin{figure}[!h] % TODO: Adjust aspect ratio
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios_constant_ae}
  \includegraphics[width=0.5\textwidth]{land_drain_scenarios_constant_ae.pdf}
\end{figure}

@@

\begin{figure}[!h] % TODO: Adjust aspect ratio
	\centering
  \caption{Simulated cases}
  \label{fig:land_drain_scenarios_fluctuating_ae}
  \includegraphics[width=\textwidth]{land_drain_scenarios_fluctuating_ae.pdf}
\end{figure}

@@

% New PP simulations with extreme Ae values for each pressure considered
% Now we capture most of the variability for open and closed
% Strong indicator that fluctating Ae is responsible for a significant portion of the variability
% Needs to be controlled better (hard)
% Or the span of values considered to give upper and lower limits on variability
% Use EPA handbook to estimate variability (pretty much can always be one OOM)
\end{comment}
